msqrob2TMT: robust linear mixed models for inferring differential abundant proteins in labelled experiments with arbitrarily complex design - Highlights

### 2025-01-31 paper/highlights.qmd
Initial commit for submission

---
title: "msqrob2TMT: robust linear mixed models for inferring differential abundant proteins in labelled experiments with arbitrarily complex design - In Brief"
authors:
  - name: Stijn Vandenbulcke
    affiliations:
      - ref: VIB
      - ref: Biomed
      - ref: UGent
  - name: Christophe Vanderaa
    affiliations:
      - ref: UGent
  - name: Oliver Crook
    affiliations:
      - ref: UK
  - name: Lennart Martens
    affiliations:
      - ref: VIB
      - ref: Biomed
  - name: Lieven Clement
    affiliations:
      - ref: UGent
    corresponding: true

@@

# In Brief

Novel msqrob2TMT workflows for differential abundance analysis of labelled proteomics data with simple and complex designs. Incorporating modular preprocessing and flexible modelling using multiple continuous and categorical variables, and their interactions. Accounting for correlations within spectra, channels, runs, mixtures, and in longitudinal designs using random effects.
Improved performance of our peptide-level and protein-level robust regression workflows over existing methods, demonstrated in two spike-in studies and one case study. Accessible through open-source Bioconductor package msqrob2 and companion GitHub page: https://github.com/statOmics/msqrob2TMT_paper.

>>>>

---
title: "msqrob2TMT: robust linear mixed models for inferring differential abundant proteins in labelled experiments with arbitrarily complex design - Highlights"
authors:
  - name: Stijn Vandenbulcke
    affiliations:
      - ref: VIB
      - ref: Biomed
      - ref: UGent
  - name: Christophe Vanderaa
    affiliations:
      - ref: UGent
  - name: Oliver Crook
    affiliations:
      - ref: UK
  - name: Lennart Martens
    affiliations:
      - ref: VIB
      - ref: Biomed
  - name: Lieven Clement
    affiliations:
      - ref: UGent
    corresponding: true

@@

# Highlights

- Statistical workflows for differential abundance analysis in labelled proteomics.
- Enhanced sensitivity and specificity.
- Flexible modelling for experiments with both simple and complex designs.
- Benchmarked against DEqMS, MSstatsTMT, and msTrawler using two spike-in datasets.
- Transparent and modular workflows through open-source Bioconductor package msqrob2.
